\documentclass{IEEEtran}

\usepackage{apacite}

\begin{document}
\title{My Bibliography using LaTex}
\author{Jian Lee}
\date{September 18, 2019}
\thispagestyle{plain}
\maketitle

\section{Personal History}
\label{sec:one}
Ji An Lee was born and raised in Seoul, Korea. She studied electrical engineering during her undergraduate studies and is now pursuing M.S. in computer science at San Jose State University. After graduating university, she joined LG Electronics as a software engineer to develop in-vehicle telematics for General Motors' Onstar project.

\section{Academic/Career Goals}
\label{sec:two}
Jian is experienced in embedded system development. She has a firm understanding of how hardware operates and the underlying software to run the hardware. During her M.S., she will leverage these knowledge to become a full-fledged back-end developer. In her first semester, she is taking the following three courses which enable her to become a better software engineer.

\begin{itemize}
	\item Advanced programming language principles autocite{CS252, Professor Thomas H. Austin, SJSU, Fall 2019}
	\item Topics in Cloud Computing autocite{CS218, Professor Kong Li, SJSU, Fall 2019}
	\item Server Web Programming autocite{CS174, Professor Fabio Di Troia, SJSU, Fall 2019}
\end{itemize}


\section{Research Topics of Interest}
\label{sec:three}
The research topics which interests Jian the most, are relevent to cloud computing and web development. During graduate studies, she plans to focus her graduate studies in these areas. In particular, she finds the following two works interesting : \cite{abrahami2019custom}, \cite{takabi2010security}.



\bibliography{References}
\bibliographystyle{ieetran}

\end{document}